\documentclass[11pt,twoside,a4paper]{article}
\begin{document}


\title{Online investigation of software failures and causal factors}

\author{Yang Wang}
\author{student id :U5833090}

\date {26th Feb 2017}

\maketitle 

\begin{abstract}

Nowadays, Information Technology is used every area, the software quality of one company strongly determines one company`s revenue and fanatical condition. The essay is going to research one software failure due to software reasons in terms of right product, done right, managed right, and monitoring issues. 
\end{abstract}

\section{Case Study}
\cite{test}
In 2013, The Federal Government of United States use HealthCare.gov system to perform their Healthcare exchange plan, however within the launch of the system,  there is only 1 percent of people finally succeed in enrolling with the website during the first week of operation. On October 20,2013 President Barack Obama remarked ``There is no sugar coating: the website has been too slow, people have been getting stuck during the application process and i think it`s fair to say that nobody?s more frustrated than i am``.


 
\section{Discussion}
Review the software failures, it seems the system have some bottleneck and fault in terms of right product, done right, manage right, and monitoring issues. 
As for the part of right product, the system neglect part of client needs and software requirements. The HealthCare.gov is designed to perform the healthcare exchange plan, thousands of americans are eligible to use this system to enrol their user information and register the plan, however the only 1 per cent of users finally managed to enrol with the site successfully, the system didn`t do well when considering there may have a circumstance that a great number of users may visit and using the website at the same time. 

For the part of done right, the system also lack enough review, testing and metrics for software improvement. From the investigation of the instance, CMS(centers for Medicare and Medicaid Services ) is responsible for the scheduling, data management and milestone project reviews. However, the CMS didn`t include many development activist or a design timeline. 

For the part of managed right and monitoring, OMB is responsible for analysing tracing and evaluating the risk of development. But OMB only coordinated with CMS to clarify policies and oversaw the budget. The process of tracing and analysing the system development is not done enough here. 

In general, it is clearly to see that the insufficient of the term of right product, done right, managed right finally lead to the bad system software quality. 



\section{Bibliography}

\bibliographystyle{plain}
\bibliography{bib4}
\end{document}
